---
title: "BINGO Sites - Topografia"
author: "Luciano Barosi"
output: html_document
---

# Topography Data

We considerar the following set of data:

1. Orange Visited Sites in first tour 20 - 24/Jun - Paraíba
2. Red dots indicated ERBs as informed by ANATEL, acording to Jun 2016.
3. Redish lines indicate fligths in the region as reported by Departamento de Controle do Espaço Aéreo (Instituto de Cartografia Aeronáutica) - 13/Oct/2016
4. Geographical data from https://www.cnpm.embrapa.br/projetos/relevobr/download/pb/pb.htm (Endeavour SRTM - 2000)
5. City shapes from Ministério do Meio Ambiente

# Paraiba Overview

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("./raster.R")
```

```{r, echo=FALSE, results='hold', fig.height=9}
panorama
```

# Zooming Sites (11km diameter)

(points 7 - 19 are prospective sites)

```{r, echo=FALSE, results='hold'}
sitiosZoom(1,0.05,25)
sitiosZoom(2,0.05,25)
sitiosZoom(3,0.05,25)
sitiosZoom(4,0.05,25)
sitiosZoom(5,0.05,25)
sitiosZoom(6,0.05,25)
sitiosZoom(7,0.05,25)
sitiosZoom(8,0.05,25)
sitiosZoom(9,0.05,25)
sitiosZoom(10,0.05,25)
sitiosZoom(11,0.05,25)
sitiosZoom(12,0.05,25)
sitiosZoom(13,0.05,25)
sitiosZoom(14,0.05,25)
sitiosZoom(15,0.05,25)
sitiosZoom(16,0.05,25)
sitiosZoom(17,0.05,25)
sitiosZoom(18,0.05,25)
sitiosZoom(19,0.05,25)
```
