---
title: "BINGO Visited sites on tour 20 - 24 Jun/2017"
author: "Luciano Barosi"
date: "24 de junho de 2017"
output: html_document
---

# Overview

We visited and measured 6 sites in total, all of them in west of Paraiba State, Alto Sertão. The maps below indicate

1. Sites Visited in blue dots
2. Circles are 10km diameter, centered in visited sites.
3. Red dots indicated ERBs as informed by ANATEL, acording to Jun 2016.
4. Pink dots are standard points for aeronavigation.
5. Yellow dashed lines indicate fligths in the region as reported by Departamento de Controle do Espaço Aéreo (Instituto de Cartografia Aeronáutica) - 13/Oct/2016
6. Maps are retrieved from OpenStreetMap

# Panorama View
```{r, echo=FALSE, results='hide'}
source("./BINGOvisited.R")
```


```{r, echo=FALSE}
map
```

# Detailed View of Sites

(Hover the mouse on the area to know the name of the site)

```{r, echo=FALSE}
m1
```

```{r, echo=FALSE}
m2
```

```{r, echo=FALSE}
m3
```

```{r, echo=FALSE}
m4
```

```{r, echo=FALSE}
m5
```

```{r, echo=FALSE}
m6
```
